---
title: "P1-Analysis-Script"
author: "Christelinda Laureijs"
date: "2024-02-19"
output:
  github_document:
    html_preview: false
  html_document:
    css: ../Templates/my-CSS-theme.css
---

```{r load-libraries, include=F}
library(here)
library(dplyr)
```

# Step 1: eEPSC data

Create a CSV file with Letter, recording ID and peak eEPSC peak amplitudes (P1 and P2) from Clampfit. This is a manual task on the lab computer.

The headings must be named `Letter`, `ID`, `P1`, and `P2`. You can copy and paste `ID`, `P1` and `P2` directly off of the results table in Clampfit.

# Step 2: Create a csv file with cell characteristics

Follow the structure of the sample `Plaintext-Cell-Characteristics.csv` file, and use the notes from your lab book to fill in information like animal, age, sex, X and Y coordinates, treatment ("None", "HNMPA", "AM251", "PPP, or "Fasting") and category (1 for PPR post HFS control, 2 for PPR after adding insulin and 3 for PPR post HFS with insulin).

# Step 3: Import CSV files

Import your new `eEPSC` csv file and your `Plaintext-Cell-Characteristics.csv` file (just change the names in the code below to match yours).

```{r import-data}
# Import new eEPSC data copied from Clampfit
new_PPR_data <- read.csv(here("Data/Raw-CSVs/20240503-Raw-CSV.csv"))


# Import CSV with info on sex, synapses, X, Y, treatment, animal, etc.
cell_characteristics <-
  read.csv(here("Data/Plaintext-Cell-Characteristics.csv"))
```

```{r view-data}
# Preview both datasets
head(new_PPR_data)
head(cell_characteristics)
```

```{r}
# Check out what letters are in the new PPR data
unique(new_PPR_data$Letter)
```

See how `Letter` is the common identifier between these two datasets?

# Step 4: Add Sex, Animal, X, Y, etc.

Merge your raw eEPSC data with the cell characteristics information. Use "Letter" as a common identifier during the merge.

```{r merge-data}
new_PPR_data_complete <-
  merge(new_PPR_data,
        cell_characteristics,
        by = "Letter")
```


```{r}
head(new_PPR_data_complete)
```


# Step 5: Add Time

Add a column called Time for each cell. Time will start at 0 and then go up to the last value in each letter (i.e. some cells lasted 30 minutes, others only lasted 20 minutes).

Each sweep is $5$ seconds, and there are $12$ sweeps in one minute. Therefore, each sweep represents $\frac{1}{12}$ of a minute.

Here is an example of what the time sequence should look like.

```{r time-sequence-example}
seq(0,1, by = 1/12)
```

```{r add-time-column}
new_PPR_data_complete <- new_PPR_data_complete %>%
  group_by(Letter) %>%
  mutate(
    Time = (row_number()-1)/12
  )
```


# Step 6: Append to main data file.

Now the dataframe contains all of the columns required to merge with the master `raw-eEPSC-data.csv` and write this to a file.
If this is your first time doing this, you don't have to do this step. Only do this once you have an existing data file and you want to add new cells onto it.

! Important: Double-check that everything is ready before doing this step, and only run this code ONCE. If you run this repeatedly, R will continue to add new rows onto your datasheet, and you will have multiple copies of each recording.

```{r}
# Rename existing raw data sheet to Raw-eEPSC-Data-Old.csv
file.rename(from = here("Data/Raw-eEPSC-Data.csv"), to = here("Data/Raw-eEPSC-Data-old.csv"))

# Import old Raw-Data sheet
raw_df <- read.csv(here("Data/Raw-eEPSC-Data-old.csv"), header = T)


# Merge old and new raw data sheets
full_PPR_data <- bind_rows(raw_df, new_PPR_data_complete)

# Write this to a file
write.csv(full_PPR_data, here("Data/Raw-eEPSC-Data.csv"), row.names=F)


# Move old datasheet to the drafts folder
# file.rename(from = here("Data/Raw-eEPSC-Data-old.csv"), to = here("Drafts","Draft-Data-Sheets",paste0(format(Sys.time(), '%Y%m%d'),"-Raw-eEPSC-Data.csv")))

# Or delete it
file.remove(here("Data/Raw-eEPSC-Data-old.csv"))


```
```{r}
# View finalized datasheet
head(full_PPR_data)

tail(full_PPR_data)
```


# Step 6: Run Thesis.Rmd file

Run Thesis.Rmd up to the chunk that says "Begin statistical analysis" (stop here, unless you want to do statistical analysis). It will use the new data file to transform and summarize the data. It will also update the following files in the `Data/Output-Data-from-R/` folder:

-   raw_df.RDS                        # Full dataset
-   pruned_df_individual_cells.RDS    # Required for pruned individual plots
-   pruned_df.RDS                     # Full pruned dataset for summary plots

If you want to save individual plots, just uncomment the code that contains functions like "make_raw_plots" and "make_pruned_plots" and set `save_choice` to "yes". It can take a long time if you have lots of plots, which is why the default is "no".

# Step 7: Generate plots document

This is an easy-to-read document that is handy for showing your cells to others.

Open the file `Quick-Plot-Viewer.Rmd` in the `Scripts` folder.

You will need to change the names a bit to reflect your specific file names and the treatments used in the experiment.

Press the "knit to HTML" button and this should generate a document containing P1 vs. Time plots (raw and pruned) for all of your cells.